### 2023-11-10 main.tex
Update main.tex

		The non-equilibrium steady state correlations can also be written as 
			\begin{equation}\label{exactCorrelation_1}
				\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\frac{1}{(1+L)!}\sum_{c_{x_{1}},\ldots,c_{x_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{1-c_{x_{k}}}\beta_{a_{k}}^{c_{x_{k}}}\left(2+L-x_{k}-\sum_{j=k}^{m}(1-c_{x_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{x_{1},\ldots,x_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{x_{k}})\right)

@@

	\mathcal{P}(0)=1-\frac{(L+1-x_{1})}{(1+L)}\qquad \mathcal{P}(1)=\frac{(L+1-x_{1})}{(1+L)}
where $\bm{\xi}=\delta_{a_{1}}^{x_{1}}$. Then, using \eqref{exactCorrelations}, we have

@@

\begin{remark} the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Subsection 4.3 of \cite{vanicat2017exact}.

@@

The proof of formula \eqref{exactCorrelations} is made in some steps:

@@

	\item In Subsection \ref{subsectionSTransf}, we introduce two similarity transformation that bring the original Hamiltonian $H$ to $H^{'}$ and $H^{''}$, with triangular and triangular-diagonal boundaries respectively. Associated to $H^{'}$ and $H^{''}$ there are two ground states denoted by $|\Psi^{'}\rangle$ and $|\Psi^{''}\rangle$ respectively. 

@@

	\item In subsection \ref{subsectionSSdual}, we invert one of the similarity transformation recovering the ground state $|\Psi^{'}\rangle$ from the explicit expression of $|\Psi^{''}\rangle$ computed in the previous step (see \eqref{ABS}).
	\item In Subsection \ref{subsection-exact} we compute the non-equilibrium steady state correlations using $|\Psi^{'}\rangle$ of the previous step. Exploiting duality to compute these correlation, we do not need the explicit expression of the steady state $|\Psi\rangle$. However, for the sake of completeness we report $|\Psi\rangle$ in Appendix \ref{appB}. 

@@

that is composed by a copy of $\mathcal{S}_{1}$ (see \eqref{S1Gen}) acting at site $x$ and with identities acting at all other sites of the chain. 

@@

that is related with the duality matrix by 

@@

 The transformation $S_{1}$ is invertible. We introduce 

@@

We introduce
 \begin{equation}
 	\mathcal{S}_{2}^{x}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\co%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
 \end{equation}
that is composed by a copy of $\mathcal{S}_{2}$ (see \eqref{S2Gen}) acting at site $x$ and with identities acting at all other sites of the chain. 
Therefore, by taking the product over the chain we obtain 
\begin{equation}\label{S2-Whole}
	S_{2}=\prod_{x=1}^{L}\mathcal{S}_{2}^{x}\dt
\end{equation}
We define 
\begin{equation}\label{HSecond}
	H^{''}=H_{\text{left}}^{''}+H_{\text{bulk}}+H_{\text{right}}^{''}\co
\end{equation}
that is related to $H'$ by
\begin{equation}
	H^{''}=S_{2}H^{'}S_{2}^{-1}\dt
\end{equation}
The boundary Hamiltonians of $H^{''}$ reads
\begin{align}\label{tri-diag-boundaryHamiltonians}
	H_{\text{left}}^{''}=e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\qquad H_{\text{right}}^{''}=e_{NN}^{L}-\mathbbm{1}\dt
\end{align}
The left one is lower triangular and depends on the differences between the boundary parameters, while the right one is diagonal. Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$, $A_{N}=e_{aN},$ and $A_{a}=e_{aa}$.
\begin{comment}
 We compute
\begin{enumerate}
	\item $A_{N}=e_{aN}$ with $a\neq 1$
	\begin{equation}
		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}e_{aN}\exp{\left(\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}=e_{aN}
	\end{equation}
\item $A_{a}=e_{aa}$ with $a\neq 1$
\begin{equation}
		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}e_{aa}\exp{\left(\sum_{c=1}^{N}\beta_{c}e_{cN}\right)}=e_{aa}+\beta_{a}e_{aN}
	\end{equation}
Indeed 
\begin{equation}
	\sum_{c=1}^{N-1}[e_{cN},e_{aa}]=\sum_{c=1}^{N-1}\beta_{c}\left(e_{ca}\delta_{aN}-e_{aN}\delta_{ca}\right)=-\beta_{a}e_{aN}
\end{equation}
\end{enumerate}
\end{comment}
Therefore, using \eqref{HT-BA} we obtain for the left boundary 
\begin{equation}
	\begin{split}
		H_{\text{left}}^{''}&=S_{2}H_{\text{left}}^{'}S_{2}^{-1}
% 		=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}
		=
		\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}-\beta_{a}e_{aN}^{1}\right)
		=
		e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\dt
	\end{split}
\end{equation}
Similarly, using again \eqref{HT-BA} we have for the right boundary 
\begin{equation}
	\begin{split}
% <<<<<<< HEAD
% 			H_{\text{right}}^{''}&=S_{2}H_{\text{right}}^{'}S_{2}^{-1}=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
% 			\\&=
% =======
			H_{\text{right}}^{''}=S_{2}H_{\text{right}}^{'}S_{2}^{-1}
% 			&=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
			=
% >>>>>>> c7f11c8ce72f62a51dea6d275334057112d03a47
			\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}-\beta_{a}e_{aN}^{L}\right)=
			e_{NN}^{L}-\mathbbm{1}\dt
	\end{split}
\end{equation}
The relation between eigenvectors with vanishing eigenvalue is 
\begin{equation}\label{S2-Inverse}
	|\Psi^{'}\rangle = S_{2}^{-1}|\Psi^{''}\rangle
\end{equation}
and $|\Psi^{''}\rangle$ solves
\begin{equation}\label{steadyS-SECOND-def}
	H^{''}|\Psi^{''}\rangle=0\dt
\end{equation}
It is convenient to introduce also the transformation
\begin{equation}\label{similarity}
	S=S_{2}S_{1}=\prod_{x=1}^{L}\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}\dt
\end{equation}
This matrix $S$ connects $H$ with $H^{''}$ by 
\begin{equation}
H=S^{-1}H^{''}S
\end{equation}
and, the relation between eigenvectors with vanishing eigenvalue is
\begin{equation}
	|\Psi\rangle=S^{-1}|\Psi^{''}\rangle\dt
\end{equation}

@@

where, for arbitrary $i\in\{1,\ldots,L\}$,  $\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{i}}\ldots,\tau_{L})$ means that the $\tau_{q_{1}},\ldots,\tau_{q_{i}}$ have been replaced by $N$. \\

@@

\begin{remark} By change the summation indices form $c\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}\in \{0,1-\delta_{\tau_{x},N}\}$ and by the by the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as 

>>>>

%{\color{blue}
%	\begin{remark}
%		The non-equilibrium steady state correlations can also be written as 
%			\begin{equation}\label{exactCorrelation_1}
%				\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\frac{1}{(1+L)!}\sum_{c_{x_{1}},\ldots,c_{x_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{1-c_{x_{k}}}\beta_{a_{k}}^{c_{x_{k}}}\left(2+L-x_{k}-\sum_{j=k}^{m}(1-c_{x_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{x_{1},\ldots,x_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{x_{k}})\right)
%\end{remark}

@@

	\mathcal{P}_{x_1}(0)=1-\frac{(L+1-x_{1})}{(L+1)}\qquad \mathcal{P}_{x_1}(1)=\frac{(L+1-x_{1})}{(L+1)}
where $\mathcal{P}_{x_1}(1)$ is the probability that a single random walk started at $x_1$ is absorbed in $\{0\}$. Then, using \eqref{exactCorrelations}, we have

@@

\begin{remark} The first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Subsection 4.3 of \cite{vanicat2017exact}.

@@

The proof of formula \eqref{exactCorrelations} is split into the following steps:

@@

	\item In Subsection \ref{subsectionSTransf}, we introduce two similarity transformations $S_1$ and  $S_2$. 
	 The first turns the Hamiltonian $H$ into $H^{'}= S_{1} H S_{1}^{-1} $ with boundary terms in a triangular form;
	 the second  turns the Hamiltonian $H'$ into $H^{''} = S_{2}H' S_{2}^{-1}$ having the left boundary in a triangular form and the right boundary is diagonal.
	Associated to $H^{'}$ and $H^{''}$ there are two ground states denoted by $|\Psi^{'}\rangle$ and $|\Psi^{''}\rangle$ respectively. 

@@

	\item In subsection \ref{subsectionSSdual}, we invert the similarity transformation $S_2$ to recover  the ground state $|\Psi^{'}\rangle$ from the explicit expression of $|\Psi^{''}\rangle$  (see \eqref{ABS}).
	\item In Subsection \ref{correlation-section} we show, using duality, that the correlations are in turn the components of the vector $|\Psi^{'}\rangle$. By exploiting a binomial formula we rewrite the correlations in terms
	as a polynomial in the left and right boundary densities with coefficients given by the absorption probabilities. For completeness, we also provide the expression of the steady state $|\Psi\rangle$ in Appendix \ref{appB}. 

@@

that is a copy of $\mathcal{S}_{1}$ (see \eqref{S1Gen}) acting at site $x$. 

@@

that is related with the bulk duality matrix by 

@@

 As the transformation $S_{1}$ is invertible,  we can introduce 

@@

We introduce
 \begin{equation}
 	\mathcal{S}_{2}^{x}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\co%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
 \end{equation}
which is a copy of $\mathcal{S}_{2}$ (see \eqref{S2Gen}) acting at site $x$. By taking the product over the chain we obtain 
\begin{equation}\label{S2-Whole}
	S_{2}=\prod_{x=1}^{L}\mathcal{S}_{2}^{x}\dt
\end{equation}
We define 
\begin{equation}\label{HSecond}
	H^{''}=H_{\text{left}}^{''}+H_{\text{bulk}}+H_{\text{right}}^{''}\co
\end{equation}
that is related to $H'$ by
\begin{equation}
	H^{''}=S_{2}H^{'}S_{2}^{-1}\dt
\end{equation}
The boundary Hamiltonians of $H^{''}$ reads
\begin{align}\label{tri-diag-boundaryHamiltonians}
	H_{\text{left}}^{''}=e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\qquad H_{\text{right}}^{''}=e_{NN}^{L}-\mathbbm{1}\dt
\end{align}
The left one is lower triangular and depends on the differences between the boundary parameters, while the right one is diagonal. Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$, $A_{N}=e_{aN},$ and $A_{a}=e_{aa}$.
\begin{comment}
 We compute
\begin{enumerate}
	\item $A_{N}=e_{aN}$ with $a\neq 1$
	\begin{equation}
		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}e_{aN}\exp{\left(\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}=e_{aN}
	\end{equation}
\item $A_{a}=e_{aa}$ with $a\neq 1$
\begin{equation}
		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}e_{aa}\exp{\left(\sum_{c=1}^{N}\beta_{c}e_{cN}\right)}=e_{aa}+\beta_{a}e_{aN}
	\end{equation}
Indeed 
\begin{equation}
	\sum_{c=1}^{N-1}[e_{cN},e_{aa}]=\sum_{c=1}^{N-1}\beta_{c}\left(e_{ca}\delta_{aN}-e_{aN}\delta_{ca}\right)=-\beta_{a}e_{aN}
\end{equation}
\end{enumerate}
\end{comment}
Therefore, using \eqref{HT-BA} we obtain for the left boundary 
\begin{equation}
	\begin{split}
		H_{\text{left}}^{''}&=S_{2}H_{\text{left}}^{'}S_{2}^{-1}
% 		=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}
		=
		\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}-\beta_{a}e_{aN}^{1}\right)
		=
		e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\dt
	\end{split}
\end{equation}
Similarly, using again \eqref{HT-BA} we have for the right boundary 
\begin{equation}
	\begin{split}
% <<<<<<< HEAD
% 			H_{\text{right}}^{''}&=S_{2}H_{\text{right}}^{'}S_{2}^{-1}=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
% 			\\&=
% =======
			H_{\text{right}}^{''}=S_{2}H_{\text{right}}^{'}S_{2}^{-1}
% 			&=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
			=
% >>>>>>> c7f11c8ce72f62a51dea6d275334057112d03a47
			\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}-\beta_{a}e_{aN}^{L}\right)=
			e_{NN}^{L}-\mathbbm{1}\dt
	\end{split}
\end{equation}
The relation between eigenvectors with vanishing eigenvalue is 
\begin{equation}\label{S2-Inverse}
	|\Psi^{'}\rangle = S_{2}^{-1}|\Psi^{''}\rangle
\end{equation}
and $|\Psi^{''}\rangle$ solves
\begin{equation}\label{steadyS-SECOND-def}
	H^{''}|\Psi^{''}\rangle=0\dt
\end{equation}
It is convenient to introduce also the transformation
\begin{equation}\label{similarity}
	S=S_{2}S_{1}=\prod_{x=1}^{L}\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}\dt
\end{equation}
This matrix $S$ connects $H$ with $H^{''}$ by 
\begin{equation}
H=S^{-1}H^{''}S
\end{equation}
and, the relation between eigenvectors with vanishing eigenvalue is
\begin{equation}
	|\Psi\rangle=S^{-1}|\Psi^{''}\rangle\dt
\end{equation}

@@

where, for arbitrary $i\in\{1,\ldots,L\}$,  $\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{i}}\ldots,\tau_{L})$ means that the $\tau_{q_{1}},\ldots,\tau_{q_{i}}$ have been replaced by $N$. 

@@

\begin{remark} By change the summation indices form $c_x\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}\in \{0,1-\delta_{\tau_{x},N}\}$ and by  the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as 
